\documentclass[11pt]{article}
\usepackage[margin=1in]{geometry}                % See geometry.pdf to learn the layout options. There are lots.
\geometry{letterpaper}                   % ... or a4paper or a5paper or ... 
%\geometry{landscape}                % Activate for for rotated page geometry
\usepackage[parfill]{parskip}    % Activate to begin paragraphs with an empty line rather than an indent
\usepackage{graphicx}
\usepackage{amssymb}
\usepackage{epstopdf}
\DeclareGraphicsRule{.tif}{png}{.png}{`convert #1 `dirname #1`/`basename #1 .tif`.png}

\newcommand{\resumename}[1]{
\begin{center} \Huge
\textsc{#1}
\end{center}}

\newcommand{\sectionheader}[1]{
{\Large
\textsc{#1}}
}

\newcommand{\resumeitem}[2]{
\begin{minipage}{0.7\textwidth}
\begin{flushleft}
\textbf{#1}
\end{flushleft}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{flushright}
\emph{#2}
\end{flushright}
\end{minipage}
\hangindent=0.05\textwidth
}

\newcommand{\resumesubitem}[2]{
\begin{minipage}{0.65\textwidth}
\begin{flushleft}
#1
\end{flushleft}
\end{minipage}
\begin{minipage}{0.3\textwidth}
\begin{flushright}
#2
\end{flushright}
\end{minipage}
\hangindent=0.05\textwidth
}

\begin{document}
%\sffamily

\resumename{Thomas Elliott}


\rule{\textwidth}{0.5pt}


\begin{minipage}[t]{0.5\textwidth}
\begin{flushleft}
88 Colin P Kelly Jr Street
\\ San Francisco, CA 94107
\end{flushleft}
\end{minipage}
\begin{minipage}[t]{0.5\textwidth}
\begin{flushright}
%714.299.7398\\
telliott@fastmail.com\\
http://www.thomaselliott.me\\
\end{flushright}
\end{minipage}

\rule{\textwidth}{0.5pt}


\sectionheader{Education}

\resumeitem{University of California, Irvine}{May 2015}
Ph.D. Sociology\\
Dissertation: \emph{The Cultural Consequences of Social Movements: The LGBT Movement and the Transformation of the Discussion of Homosexuality in Mainstream Newspapers}\\
Chair: Edwin Amenta

\resumeitem{University of California, Irvine}{Fall 2009}
M.A. Sociology\\
Thesis: \emph{The Queer Movement and the Media: New York Times Coverage of LGBT and AIDS Organizations 1969-2007}

\resumeitem{University of Texas at Dallas}{May 2006}
B.S. Interdisciplinary Studies - Physics \& Chemistry Education\\
Honors Thesis: \emph{Providing a Safe Space: Creating a safer school climate for gay, lesbian, bisexual, transgender, and questioning youth.}

\sectionheader{Interests}

\textbf{Research Interests:} Social Movements, Sexualities, Culture, Computational Social Science, Quantitative Methodologies, Social Network Analysis

\textbf{Programming Languages:} R, Python, Stata, Javascript, PHP, MySQL

\textbf{Teaching Interests:} Statistics, Quantitative Methodologies, Social Movements, Political Sociology, Social Problems, Sociology of Sexualities, Sociology of Gender, Computational Social Science

\sectionheader{Current Position}

\resumeitem{Data Scientist, GitHub}{2017-Present}


\sectionheader{Publications}

Forthcoming - Amenta, Edwin, and Thomas Alan Elliott. ``What Drives Progressive Policy? Institutional Politics, Political Mediation, Policy Feedbacks and Early U.S. Old-Age Policy.'' \textit{Sociological Forum}. 

Forthcoming - Amenta, Edwin, Thomas Alan Elliott, Nicole Shortt, Amber Celina Tierney, Didem Turkoglu, Burrel Vann Jr. ``Institutional Mediation, Why Movement Organizations Receive Substantive Coverage, and the 1960s Civil Rights Movement.'' \textit{Mobilization}.

Forthcoming --- Amenta, Edwin, and Thomas Alan Elliott. ``All the Right Movements?
Mediation, Rightist Movements, and Why U.S. Movements Received Extensive Newspaper Coverage.'' \textit{Social Forces}. 

2018 --- Elliott, Thomas and Jennifer Earl. "Kids These Days: Supply and Demand for Youth Online Political Engagement." \textit{Digital Media \& the Future(s) of Democracy.} Democracy, Citizenship, and Constitutionalism Series. University of Pennsylvania Press.

2018 -- Elliott, Thomas and Jennifer Earl. ``Organizing the Next Generation: Youth Engagement with Activism Inside and Outside of Organizations.'' \textit{Social Media + Society}.

2017 --- Earl, Jennifer, Thomas V. Maher, and Thomas Alan Elliott. ``Youth, Activism, and Social Movements.'' \textit{Sociology Compass} 11:e12465.

2017 --- Amenta, Edwin, Thomas Alan Elliott, Nicole Shortt, Amber Celina Tierney, Didem Turkoglu, Burrel Vann Jr. ``From bias to coverage: What explains how news organizations treat social movements.'' \textit{Sociology Compass}. 

2017 --- Elliott, Thomas Alan, Jennifer Earl, and Thomas V. Maher, ``Recruiting Inclusiveness: Intersectionality, Social Movements, and Youth Online.'' \textit{Research in Social Movements, Conflicts, and Change}.

2016 --- Edwin Amenta, Thomas Alan Elliott, and Amber Celina Tierney, ``Political Reform and the Newspaper Coverage of U.S. Movements in Depression, Recession, and Historical Perspective.'' \textit{Mobilization} 21(4):393-412.

2016 --- Elliott, Thomas Alan and Jennifer Earl. ``Online Protest Participation and the Digital Divide: Modeling the Effect of the Digital Divide on Online Petition Signing.'' \textit{New Media and Society}.

2016 --- Elliott, Thomas Alan, Edwin Amenta, and Neal Caren, ``Recipes for Attention: Policy Reforms, Crises, Organizational Characteristics, and the Newspaper Coverage of the LGBT Movement, 1969-2009.'' \textit{Sociological Forum}. 

2014 --- Kane, Melinda, and Thomas Alan Elliott. ``Turning to the Courts: A Quantitative Analysis of the Gay and Lesbian Movement's Use of Legal Mobilization.'' \textit{Sociological Focus} 47(4):219-231.

2014 --- Treas, Judith, and Thomas A. Elliott. ``Sex, Family and Social Change." In Judith Treas, Jacqueline Scott, and Martin P.M. Richards. \textit{The Wiley-Blackwell Companion to Sociology of Families (2nd edition)}. Oxford: Wiley-Blackwell Publishers. Pp. 527-546.

2012 --- Amenta, Edwin, Beth Gharrity Gardner, Amber Celina Teirney, Anaid Yerena, and Thomas Elliott. ``A Story-Centered Approach to the Newspaper Coverage of High-Profile SMOs.'' \textit{Research in Social Movements, Conflicts, and Change} 33:83-107





\sectionheader{Prior Employment}

\resumeitem{Data Science Fellow, Insight}{2017}

\resumeitem{Lecturer, California State University, Channel Islands}{2016-2017}
\resumesubitem{Courses Taught: Social Movements, Statistical Applications in Political Science}{}

\resumeitem{Postdoctoral Research Scholar, University of Arizona}{2015-2016}
\resumesubitem{Youth Activism Project (with Jennifer Earl)}{}

\resumeitem{Department of Sociology's Statistics Consultant, University of California, Irvine}{2014-2015}

\resumeitem{Research Assistant, University of California, Irvine}{2010-2015}\\
\resumesubitem{Supervisors: Edwin Amenta, Nina Bandelj, Francesca Polletta}{}

\resumeitem{Instructor, University of California, Irvine}{2010-2014}\\
\resumesubitem{Courses Taught: Statistics Refresher Course, Sociology of Sexuality}{}


\resumeitem{Teaching Assistant, University of California, Irvine}{2007 - 2013}


\sectionheader{Presentations}

2015 --- ``Strategies, Stories, and the Quality of News Coverage of the Civil Rights Movement.'' \textit{American Sociological Association}, Chicago, IL, with Edwin Amenta, Nicole Clorinda Shortt, and Amber Celina Tierney.

2015 --- ``Cultural Tastes and Race: Interest-Based Boundaries Among Daters.'' \textit{American Sociological Association}, Chicago, IL, with Matt Rafalow (presenting) and Cynthia Feliciano.

2014 --- ``Perverts, Homosexuals, Gays, and Lesbians: Newspaper Coverage of Homosexuality, 1950-2010.'' \textit{American Sociological Association}, San Francisco, CA. 

2014 --- ``Economic Protest Movements of the Great Depression and Great Recession.'' \textit{American Sociological Association}, San Francisco, CA, with Edwin Amenta and Amber Tierney.

2014 --- ``The Cultural Consequences of Social Movements: The LGBT Movement and the Transformation of Discourse About Homosexuality.'' \textit{Young Scholars in Social Movements Conference}, Notre Dame.

2013 --- ``Paths to Coverage: Newspaper Coverage of the LGBT Movement, 1969-2009.'' \textit{American Sociological Association}, New York, NY, with Edwin Amenta and Neal Caren.

2013 --- ``Good Coverage: SMO's Sustained and Substantive Coverage in Major Newspapers.'' \textit{American Sociological Association}, New York, NY, with Edwin Amenta, Neal Caren, and Amber Celina Tierney.

2012 --- ``Policy Influence on Social Movements: Newspaper Coverage of LGBT SMOs.'' \textit{American Sociological Association}, Denver, CO, with Edwin Amenta and Neal Caren.

2011 --- ``Dramatic Action, Assertive Action, and Securing Demands: Newspaper Coverage of SMOs and the Townsend Plan.'' American Sociological Association, Las Vegas, NV, with Edwin Amenta, Beth Gharrity Gardner, Amber Celina Tierney, and Anaid Yerena.

2011 --- ``Policy Influence on Social Movements: The Impact of Policy Reforms on LGBT and AIDS Organizations.'' Roundtable at American Sociological Association annual meeting, Las Vegas, NV.

2011 --- ``Gaining Attention: Explaining Newspaper Coverage of the LGBT and AIDS Movement 1969-2007.'' Pacific Sociological Association annual meeting, Seattle, WA.

2007	 --- ``Turning to the Courts: A Quantitative Analysis of the Gay and Lesbian Movement?s Use of Legal Mobilization.'' Southern Sociological Society annual meeting, Atlanta, GA, as second author (presented by Dr. Melinda Kane).

\sectionheader{Invited Presentations}

2016 --- ``Recruiting the News: A Topic Modeling and Discourse Network Analysis of Mainstream Newspaper Coverage of Homosexuality, 1950-2010, \textit{SCANCOR Monday Seminar Series}, Stanford University.

2014 --- ``U.S. Movements in the Great Depression and Great Recession: Why They Took Off and Why There Were So Different.'' \textit{The Future of Democracy After Neoliberalism: Social Movements in a Globalizing World}, Kyoto University, with Edwin Amenta and Amber Tierney (presented by Edwin Amenta). 

2014 --- ``Politics, Movements, and Policy: Recipes for Influence over U.S. Old-Age Policy in Its Formative Years.'' \textit{Voters, Protest and Policies: Bridging Public Opinion, Social Movement Outcomes and Policy Responsiveness Research}, University of Leicester, with Edwin Amenta and Charles Ragin (presented by Edwin Amenta).

2013 --- ``Demonstrating Time Series Analysis With Newspaper Coverage of LGBT Organizations.'' Statistics Group, UCI.

2013 --- ``Fuzzy Set Qualitative Comparative Analysis: A Data Analysis Example.'' Statistics Group, UCI.

2013 --- ``Fuzzy Set Qualitative Comparative Analysis: An Introduction.'' Statistics Group, UCI.



\sectionheader{Awards, Grants, and Fellowships}

2015 --- Excellence in Mentorship Award, Department of Sociology, UCI\\
2014 --- Excellence in Research Award, Department of Sociology, UCI\\
2014 --- James Harvey Scholar Award, \$8,000\\
2013 --- Graduate Dean's Dissertation Fellowship, \$10,000\\
2012 --- Associate Dean's Fellowship, \$10,500\\
2007 --- Social Science Merit Award (five years of funding, including 3 quarters of fellowship and 12 quarters of teaching assistantship)\\


\sectionheader{Professional Activities \& Affiliations}

Manuscript Reviewer: \textit{Mobilization}, \textit{Social Science Research}, \textit{International Journal of Comparative and Applied Criminal Justice}, \textit{Journal of Business Research}, \textit{Social Problems}, \textit{Sociology Compass}

Book Reviewer: \textit{Mobilization}

2007-current:	Member; American Sociological Association\\
2007-2012:	Member; Pacific Sociological Association\\
2009-2013:	Cohort Representative to Sociology Graduate Student Association






\end{document}  